---
title: "EDA"
subtitle: "Exploring AC Survey"
author: "Dylan Bay"
date: today
format:
    html:
        toc: true
        df-print: paged
        code-fold: true  # Code hidden by default
        embed-resources: true
        code-summary: "Show the code"
theme: simplex
editor: visual
---

```{r}
#| label: setup
#| include: false

# From Cleaning.R
library(dplyr)
library(readr)
library(tidyr)
library(stringr)
library(sf)  
library(rnaturalearth) 
library(here)
library(lubridate)

# Loaded here
library(forcats)
library(ggplot2)
library(cowplot)
library(patchwork)
library(skimr)
library(naniar)

# Options
knitr::opts_chunk$set(  
fig.width = 8,
fig.height = 5,
fig.align = "center",
dpi = 300
) # beyond YAML defaults
options(scipen = 999)
theme_set(theme_cowplot())

#TODO: add package imports from inside up here and eliminate superfluous ones
```

# Introduction

On Tues, May 24, 2022 I ran a survey on the Assassin's Creed community on Reddit ([link](https://www.reddit.com/r/assassinscreed/comments/uwy6rd/which_ac_game_really_does_the_subreddit_like_the/)). The survey was designed pretty narrowly with one major goal, to understand the most popular games in the franchise and what made them popular, but also to see if there were any special links between games (for example, the franchise is usually roughly divided into 3 "eras" based on the look and feel of the games and their developer choices, AC1 thru AC3, AC4 thru AC Syndicate, AC Origins thru AC Valhalla). For simplicity, I only allowed the "mainline" games to be rated. To improve completion rates, I designed it to be both minimal and conditional: first respondents would select all the games they had played, and then they would rate each on Story, Gameplay, and Overall. The survey was conducted with Qualtrics and the exact phrasing was as follows:

> (Reddit title) Which AC game really DOES the subreddit like the most? Take the (unofficial) survey!

> (Landing page) Thanks in advance! Please note this is NOT an official survey and in no way is affiliated with the publisher or the subreddit. It's just something fun that will be have results published on the subreddit, to get the data behind the commonly asked questions: Which Assassin's Creed game is the best? Which one has the best story or gameplay? Which should I buy? I've kept the survey nice and short and to the point!

> (First question text) Which Assassin's Creed games have you played and would thus like to rate on the next page? Select all that apply.

> "Assassin's Creed (2007)", "Assassin's Creed II (2009)", "Assassin's Creed: Brotherhood (2010)", "Assassin's Creed: Revelations (2011)", "Assassin's Creed III (2012)", "Assassin's Creed IV: Black Flag (2013)", "Assassin's Creed: Rogue (2014)", "Assassin's Creed: Unity (2014)", "Assassin's Creed: Syndicate (2015)", "Assassin's Creed: Origins (2017)", "Assassin's Creed: Odyssey (2018)", "Assassin's Creed: Valhalla (2020)"

> (Second question text) Reviews of the games generally seem to boil down to feedback on the Story and Gameplay, which are often different. You'll also of course be asked for an overall rating for the game, how much you personally enjoyed playing it overall (not necessarily how much you'd recommend it to others!) Please rate on a classic 1-10 scale. NOTE: Please rate the game based on how it was when you played it; or if you've played a while or several times, please rate based on final patched version with any purchased DLC.

I collected 324 responses. 240 fully completed responses, 5 with a minor missing response, and 79 responses that included which games they played but didn't continue to the subratings section.

This notebook contains an exploration of the data, data-based answers to several common community claims and questions, and further statistical analysis. `Cleaning.R` is referenced and contains the core import and most of the augmentation and shaping logic. A bit of additional reshaping and augmentation occurs in this script. `SelectionEffectsViz.R` explores reliability of the data to the extent possible.

# Import

```{r}
#| label: load-data

source(here::here("Cleaning.R"))
```

# EDA

Three ways to visualize and categorize the geographic makeup of respondents, sourced from IP address.


```{r}
#| label: country_eda

country.gg <- df %>%
   count(CountryName) %>%
  filter(n > 1) |> 
   ggplot(aes(x = n, y = fct_reorder(CountryName, n), fill = CountryName)) +
   geom_col() +
   labs(x = "Number of Responses (n > 1)", y = "Country") +
  theme(legend.position = "none")
subregion.gg <- df %>%
   count(Subregion) %>%
   ggplot(aes(x = n, y = fct_reorder(Subregion, n), fill = Subregion)) +
   geom_col() +
   labs(x = "Number of Responses", y = "Subregion")
wbregion.gg <- df %>%
   count(WBRegion) %>%
   ggplot(aes(x = n, y = fct_reorder(WBRegion, n), fill = WBRegion)) +
   geom_col() +
   labs(x = "Number of Responses", y = "World Bank Subregion")
country.gg 
subregion.gg
wbregion.gg
# note that WBRegion does not perfectly nest in Subregion due to a few MENA countries (Turkey, Israel, Saudi Arabia)
```

# Transformations and Missing Data

```{r}
#| label: missing-data

df_missing <- df |> 
  filter(if_all(ends_with("_1"), is.na))  # req recent version: dpylr 1.2+
# 30 records didn't proceed to the second question - that's a 90.7% rate to pass to the next set. Decent.
# wait - I did that wrong I think - it's acutally 79??
# also not really relevant but 4 years later reddit shows 6.4k views on the survey page. 
# While obviously that's cumulative (so really is higher), it implies maybe a 5% click-through rate? decent.

# # let's see if we maybe have any problematic completions? 
# because remember we have a whole set of games-played only, and then full ratings... but did any FULL raters give up?
# this is kinda tricky to code with branching logic...

# To do this let's do a two-step transform of the grain: from respondent-rows, to individual response-rows
#  (with a metadata column identifying the question), then re-block (wider) as question-rows

df_long <- df |> 
  pivot_longer(
    cols = contains("_"),
    names_to = c("group", "question"),
    names_sep = "_"
  ) |> 
  pivot_wider(
    names_from = question,
    values_from = value
  )

# this answers: did anyone forget or decline to fill in one of the three subquestions (within a game) randomly?
partial_within_game <- df_long |> 
  filter(Intro == 1) |> 
  filter(is.na(`1`) | is.na(`2`) | is.na(`3`)) |>  
  select(c("ResponseId", "IntroList", "group", "Intro", `1`, `2`, `3`, "Progress", "Duration")) |> 
  filter((is.na(`1`) + is.na(`2`) + is.na(`3`)) < 3)
# yes, three people. will need to consider how to handle this, because will (slightly) affect a few calculations
# note that all three of these people DID fully rate all the rest, it's just these randomly missing single sub-q's
# c("R_1ikUGhQjZS6RZJt", "R_BPzLWS3pTSYFU2J", "R_Uu9SV5hqekMiW8V")

# usually, either someone drops the survey entirely when reaching the non-Intro question, OR fills it ALL out.
# this answers: did anyone fill out only SOME of the follow-ups?
partial_within_list <- df_long |> 
  filter(Intro == 1) |>    # the question was supposed to have been filled out, and...
  group_by(ResponseId) |>  # on a per person basis...
  filter(
    any(is.na(`1`) & is.na(`2`) & is.na(`3`)) &   # does the person have a group that's all missing AND
    any(!is.na(`1`) | !is.na(`2`) | !is.na(`3`))  # does the person have at least one group with a real answer?
  ) |>
  ungroup()
# yes, two people neglected to answer one game, randomly
# c("R_1Ow4KSy0Od9qDxH", "R_3ncpah7gt2PAX4m")

# I could easily pull() the vectors of ID's but since this is a notebook I think it's fine to hardcode this small group
partial_response_Ids <- c("R_1ikUGhQjZS6RZJt", "R_BPzLWS3pTSYFU2J", "R_Uu9SV5hqekMiW8V", 
                          "R_1Ow4KSy0Od9qDxH", "R_3ncpah7gt2PAX4m")
# Thus for questions that require both sets of data and no partials of any kind, "dff" for "df full"
dff <- df |> 
  filter(!(ResponseId %in% partial_response_Ids),
         !if_all(ends_with("_1"), is.na))
# later are pivoted - bring up here?
  
```

# Data Reliability and Time Shift

```{r}
#| label: response-time-shift

#TODO: clean up comments in this section
library(dplyr)
library(effsize)

# 1. Bucket the days and drop the rest
df_bucketed <- df %>%
  mutate(DayBucket = case_when(
    RecordedDay == 24 ~ "Day 24",
    RecordedDay == 25 ~ "Day 25",
    RecordedDay %in% c(26, 27) ~ "Days 26-27",
    RecordedDay %in% c(28, 29) ~ "Days 28-29",
    TRUE ~ "Drop"
  )) %>%
  filter(DayBucket != "Drop") %>%
  mutate(DayBucket = factor(DayBucket, levels = c("Day 24", "Day 25", "Days 26-27", "Days 28-29")))

# 2. Generate all unique pairs of your buckets
buckets <- levels(df_bucketed$DayBucket)
pairs <- combn(buckets, 2, simplify = FALSE)

# 3. Calculate Cliff's Delta for each pair
results <- lapply(pairs, function(p) {
  # Subset data to just the two groups we are comparing
  subset_df <- df_bucketed %>% 
    filter(DayBucket %in% p) %>%
    mutate(DayBucket = droplevels(DayBucket)) # cliff.delta strictly expects exactly 2 levels
  
  # Run the test
  cd <- cliff.delta(TotalPlayed ~ DayBucket, data = subset_df)
  
  # Extract the useful bits into a clean row
  data.frame(
    Group_1 = p[1],
    Group_2 = p[2],
    Cliffs_Delta = round(cd$estimate, 3),
    CI_Lower = round(cd$conf.int[1], 3),
    CI_Upper = round(cd$conf.int[2], 3),
    Magnitude = as.character(cd$magnitude)
  )
})

# 4. Combine and view the results
cliff_results <- bind_rows(results)
print(cliff_results)

# this is % overlapping prob
# Instead of just saying "Day 1 and Day 2 are different," Cliff's Delta quantifies how much they overlap. It ranges from
# -1 to 1. A value of 0 means the distributions are completely overlapping; 1 or -1 means there is no overlap at all. It
# is incredibly easy to explain to an audience: "A randomly selected person from Day 1 has a 30% higher chance of having
# played more games than a person from Day 2."

# long story short: mostly there is a noticeable Day 1 effect, though still only so-so in strength
```

COMPLEMENT to the above:

```{r}
#TODO: consider either moving above into the external script, or bringing all of them into here.
source("SelectionEffectsViz.R")
```

```{r}
#TODO: 
# did we get excessive dropout due to anticipated fatigue?
# lm in_df_missing ~ TotalPlayed ?
```

# Principal Visualization

```{r}
#| label: subscore-pivots

library(ggdist)  # may conflict ggridges; resolve if combining SelectionEffectsViz.R

# use dff to for full subdata only
# prep for visualization by pivoting to tidy standards: game+rater grain and single-subrating grain
dff_games <- dff |> 
  pivot_longer(
    cols = contains("_"),
    names_to = c("GameNum", "question"),
    names_sep = "_"
  ) |> 
  pivot_wider(
    names_from = question,
    values_from = value
  ) |> 
  rename(Story = `1`, Gameplay = `2`, Overall = `3`, Played = "Intro") |> 
  mutate(GameNum = factor(as.numeric(GameNum), levels = 1:12, labels = short_gamenames))
dff_responses <- dff |> 
  pivot_longer(
    cols = contains("_"),
    names_to = c("GameNum", "Subquestion"),
    names_sep = "_",
    values_to = "Rating"
  ) |> 
  mutate(Subquestion = replace_values(Subquestion, from = c("1", "2", "3"), 
                                      to = c("Story", "Gameplay", "Overall")),
         GameNum = factor(as.numeric(GameNum), levels = 1:12, labels = short_gamenames)) |> 
  filter(Subquestion != "Intro")
```

```{r}
#| label: violin-facet
#| warning: false

library(ggbeeswarm)
dff_responses |> 
  ggplot(aes(x = Subquestion, y = Rating, fill = Subquestion, color = Subquestion)) +
  geom_violin(trim = FALSE, alpha = 0.7, color = NA) + 
  geom_quasirandom(alpha = 0.2, size = 0.8, dodge.width = 0.8) +
  facet_wrap(~GameNum) +
  theme_cowplot() + 
  scale_fill_manual(values = c("Story" = "#1f78b4", "Gameplay" = "#6a3d9a", "Overall" = "#33a02c")) + 
  scale_color_manual(values = c("Story" = "#1f78b4", "Gameplay" = "#6a3d9a", "Overall" = "#33a02c")) +
  theme(
    panel.grid.major.y = element_line(color = "grey92", linewidth = 0.5),
    axis.text.x = element_blank(), 
    axis.ticks.x = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.title = element_text(face = "bold")
  ) +
  guides(
    fill = guide_legend(title.position = "left", title.vjust = 0.5, nrow = 1),
    color = guide_legend(title.position = "left", title.vjust = 0.5, nrow = 1)
  ) +
  scale_y_continuous(breaks = c(2, 4, 6, 8, 10), limits = c(0, 10)) +
  xlab("")
```

Okay, that's a good visual. Some observations: AC1 and AC2 are carried and dominated in overall score by story; Brotherhood, weirdly, is the opposite. AC1 is pretty notable for having gameplay that is mid at the verybest. Revelations is a bit polarizing within the high side regarding story. AC3 starts to noticeably droop in scores, but Black Flag seems to deserve high praise all around. Starting with Rogue and Unity, we start to see story sag for a while, culminating with a VERY panned Syndicate story, being pulled much more sharply towards 7's in story and this appears to drag down the overall ratings. Interestingly, for the most part gameplay seems to keep the overall ratings from excessive deterioration. Origins seems to be a clear return to form with the shapes up with the best of them, although there are clearly some detractors. Odyssey has a clearly softer story and Valhalla even worse; Odyssey seems to have some polarizing gameplay but Valhalla seems an even riskier bet. Looking overall, about half of the games had significant numbers of "hated" story ratings.

IDEA: Look at 10/10's proportions alone?

```{r}
#| label: top10-shares

library(scales)
dff_responses |> 
  filter(!is.na(Rating)) |> 
  mutate(GameNum = fct_recode(GameNum, !!!setNames(short_gamenames, community_gamenames))) |> 
  group_by(GameNum, Subquestion) |> 
  summarize(PerfectScoreProportion = mean(Rating == 10), .groups = "drop") |>
  ggplot(aes(x = GameNum, y = PerfectScoreProportion, fill = Subquestion)) +
  geom_col(position = position_dodge(), color = "black", linewidth = 0.2, alpha = 0.8) +
  scale_fill_manual(values = c("Story" = "#1f78b4", "Gameplay" = "#6a3d9a", "Overall" = "#33a02c")) +
  scale_y_continuous(labels = label_percent(accuracy = 1), expand = expansion(mult = c(0, 0.05)),
                     limits = c(0,.5)) +  # consider to 1 for 100% scale
  theme_cowplot() + 
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    panel.grid.major.y = element_line(color = "grey95", linewidth = 0.5),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")
  ) +
  guides(fill = guide_legend(title.position = "left", title.vjust = 0.5, nrow = 1)) +
  labs(
    x = "",
    y = "Proportion of 10/10 Ratings",
    fill = "Subquestion"
  )
```




```{r}
#| label: overall-violins

dff_responses |> 
  filter(Subquestion == "Overall") |> 
  mutate(GameNum = fct_recode(GameNum, !!!setNames(short_gamenames, community_gamenames))) |> 
  ggplot(aes(x = GameNum, y = Rating, fill = GameNum, color = GameNum)) +
  geom_violin(alpha = .7, quantile.linetype = 1, scale = "width", quantiles = 0.5) +
  theme_cowplot() + 
  scale_fill_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_color_manual(values = setNames(ac_palette, community_gamenames)) +
  theme(axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")) +
  scale_y_continuous(breaks = 1:10) +
  xlab("") +
  ylab("Overall Game Rating") +
  labs(title = "\"General/Overall\" Enjoyment Rating Distributions",
       subtitle = "Scaled to identical width, out of those who rated the game only")
```


```{r}
#| label: overall-bubbles

library(ggforce)
# alternate visualization
dff_responses |>
  filter(Subquestion == "Overall") |>
  mutate(GameNum = fct_recode(GameNum, !!!setNames(short_gamenames, community_gamenames))) |>
  count(GameNum, Rating) |>
  ggplot(aes(x = GameNum, y = Rating, size = n, fill = GameNum, color = GameNum)) +
  geom_point(alpha = 0.7, shape = 21, stroke = 0.5) +
  theme_cowplot() +
  scale_fill_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_color_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_size_area(max_size = 18) +       # area scaling is more honest than radius
  scale_y_continuous(breaks = 1:10) +
  theme(axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")) +
  xlab("") +
  labs(title = "Overall Rating Distributions",
       subtitle = "Bubble size = number of responses, out of those who rated the game only") +
  guides(fill = "none", color = "none", size = "none")

# explore compressing the distance between columns in bubblechart and solving top cutoff issue
```

# Rating Counts

```{r}
#| label: played-barplot

# we were getting ahead of ourselves - how many people even PLAYED each of these games? huge disparities?
played_barplot <- df_long |> 
  filter(!(ResponseId %in% partial_response_Ids)) |> 
  drop_na() |> 
  mutate(Game = factor(as.numeric(group), levels = 1:12, labels = community_gamenames),
         PlayedIt = Intro) |> 
  ggplot(aes(x = Game, fill = Game, color = Game)) +
  geom_bar(alpha = .9) +
  theme_cowplot() +
  scale_fill_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_color_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_y_continuous(breaks = seq.int(0, 120, 20)) +
  theme(axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")) +
  xlab("") +
  ylab("Counts") +
  labs(title = "Total responses (full ratings)") +
  guides(fill = "none", color = "none", size = "none")
played_barplot

```

```{r}
# ordered by descending
played_barplot <- df_long |> 
  filter(!(ResponseId %in% partial_response_Ids)) |> 
  drop_na() |> 
  mutate(Game = factor(as.numeric(group), levels = 1:12, labels = community_gamenames),
         Game = fct_infreq(Game),
         PlayedIt = Intro) |> 
  ggplot(aes(x = Game, fill = Game, color = Game)) +
  geom_bar(alpha = .9) +
  theme_cowplot() +
  scale_fill_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_color_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_y_continuous(breaks = seq.int(0, 120, 20)) +
  theme(axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, color = "black") +
  xlab("") +
  ylab("Counts") +
  labs(title = "Total responses (full ratings)") +
  guides(fill = "none", color = "none", size = "none")
played_barplot
```


```{r}
# superseded by below in terms of answering the right question, but kept in case useful later

# played_norate_barplot <- df_missing |> 
#   pivot_longer(
#     cols = ends_with("_Intro"),
#     names_to = c("Game", "Intro"),
#     names_sep = "_"
#   ) |> 
#   filter(!is.na(value)) |> 
#   select(c(ResponseId:RecordedDate, TotalPlayed:Game, value)) |> 
#   rename(PlayedIt = value) |> 
#   mutate(Game = factor(as.numeric(Game), levels = 1:12, labels = community_gamenames)) |> 
#   ggplot(aes(x = Game, fill = Game, color = Game)) +
#   geom_bar(alpha = .9) +
#   theme_cowplot() +
#   scale_fill_manual(values = setNames(ac_palette, community_gamenames)) +
#   scale_color_manual(values = setNames(ac_palette, community_gamenames)) +
#   scale_y_continuous(breaks = seq.int(0, 120, 20)) +
#   theme(axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")) +
#   xlab("") +
#   ylab("Counts") +
#   labs(title = "Total responses (played it but didn't rate it)") +
#   guides(fill = "none", color = "none", size = "none")
# 
# played_barplot / played_norate_barplot
```


```{r}
# this needs review as I'm not 100% sure what it all does (the rare exception here)

# Extract full responses
df_full_status <- df_long |> 
  filter(!(ResponseId %in% partial_response_Ids)) |> 
  drop_na() |> 
  mutate(Game = factor(as.numeric(group), levels = 1:12, labels = community_gamenames),
         Status = "Rated") |> 
  select(Game, Status)

# Extract partial responses
df_partial_status <- df_missing |> 
  pivot_longer(
    cols = ends_with("_Intro"),
    names_to = c("Game", "Intro"),
    names_sep = "_"
  ) |> 
  filter(!is.na(value)) |> 
  mutate(Game = factor(as.numeric(Game), levels = 1:12, labels = community_gamenames),
         Status = "Did Not Rate") |> 
  select(Game, Status)

# Combine into one dataframe
df_combined <- bind_rows(df_full_status, df_partial_status)

chisq_norate <- chisq.test(table(df_combined$Game, df_combined$Status))

ggplot(df_combined, aes(x = Game, fill = Status)) +
  geom_bar(position = "fill", alpha = .9) +
  theme_cowplot() +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")) +
  xlab("") +
  ylab("Proportion") +
  labs(title = "Proportion of players who completed ratings by game",
       subtitle = sprintf("Chi-squared = %.2f, df = %d, p = %.3f; not abnormal and thus unlikely to influence ratings", 
                      chisq_norate$statistic, chisq_norate$parameter, chisq_norate$p.value)) +
  scale_fill_manual(values = c("Rated" = "#2F4F4F", "Did Not Rate" = "#B22222")) 

```

As the chart explains, likelihood to continue on to rate the game doesn't appear to differ so much that there is a disparity. In other words, no significant selection effect in progressing to the subquestions on the survey.

# Games Played Count

```{r}
dff_user_level <- dff |>
  arrange(TotalPlayed) |>
  mutate(
    prop_users = row_number() / n(),
    prop_ratings = cumsum(TotalPlayed) / sum(TotalPlayed)
  )

#TODO: Make me prettier because this is an important plot
ggplot(dff_user_level, aes(x = factor(TotalPlayed))) +
  geom_bar(fill = "steelblue", color = "white") +
  theme_minimal() +
  labs(
    title = "Volume of Ratings per User",
    x = "Number of Games Rated",
    y = "Number of Users"
  )

ggplot(dff_user_level, aes(x = prop_users, y = prop_ratings)) +
  # The "Perfect Equality" line
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "grey") +
  # The actual concentration curve
  geom_line(color = "firebrick", linewidth = 1) +
  # Formatting to percentages
  scale_x_continuous(labels = label_percent(), expand = c(0,0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0,0)) +
  theme_minimal() +
  labs(
    title = "Concentration of Ratings",
    subtitle = "Cumulative % of users vs. Cumulative % of ratings contributed",
    x = "% of Users (Sorted by TotalPlayed)",
    y = "% of Total Ratings Provided"
  )
```

We should note that the top 19% (i.e. those that played 12 games) contributed the top 46% of game ratings (top 26% gives top 61% if you relax the cutoff to 11). 

Also, a full 50% of users who rated a game had only played a single one! This contributed only 10% of the ratings. 

This is unfortunately a major limitation, I realize! There's a limited set of players who have experienced both the classic and the RPG era of games...

TODO: Would be kind of interesting to see an overlay of 1-gamers, vs mid-gamers, vs big-gamers (11 & 12). E.g. stacked bar? Ridge plot? Dunno. And also see if there is a correlation between the SelectionEffects (when they rated and such). perhaps add a category tag

```{r}
# which games were missing for the otherwise hardcore fans?
dff_user_level |> 
  filter(TotalPlayed == 11) |> 
  pivot_longer(
    cols = ends_with("_Intro"), 
    names_to = "GameName", 
    values_to = "PlayedStatus"
  ) |> 
  filter(is.na(PlayedStatus)) |> 
  select(ResponseId, GameName) |> 
  arrange(GameName) #|> View()
```

Out of those 11s? Just for my curiosity, 7 missing Valhalla, 7 missing Rogue, 5 missing AC1, which makes sense

# Direct Comparison

(IDEA: interactive select a few to compare side by side in this type of setup?)

```{r}
# spot-check about a guy who claims that AC1 is better than AC2; measure dimension-wise and strict dominance. 
# could fold this into a function for direct comparisons? Or make into a tool?
dff |> 
  filter(`1_Intro` == 1 & `2_Intro` == 1) |> 
  select(c(ResponseId:`2_3`, TotalPlayed:RecordedWeekday)) |> 
  mutate(PreferACIStory = ifelse(`1_1` < `2_1`, 1, 0), 
         PreferACIGameplay = ifelse(`1_2` < `2_2`, 1, 0), 
         PreferACIOverall = ifelse(`1_3` < `2_3`, 1, 0),
         PreferACIUniversally = ifelse(PreferACIStory == 1 & PreferACIGameplay == 1 & PreferACIOverall == 1, 1, 0)) |> 
  summarise(across(starts_with("Prefer"), mean))
```


# Era Categories

```{r}
#TODO: as mentioned before, consider putting this elsewhere

dff_eras <- dff_games |> 
  mutate(
    game_idx = as.integer(GameNum),
    CatMechanics = case_when(
      game_idx <= 7 ~ "Social Stealth",
      game_idx %in% 8:9 ~ "Transition",
      game_idx >= 10 ~ "RPG"
    ),
    CatMechanics = factor(CatMechanics, levels = c("Social Stealth", "Transition", "RPG")),
    
    CatNarrative = case_when(
      game_idx <= 5 ~ "Desmond",
      game_idx %in% 6:9 ~ "Anthology",
      game_idx >= 10 ~ "Layla"
    ),
    CatNarrative = factor(CatNarrative, levels = c("Desmond", "Anthology", "Layla")),
    
    CatCommunity = case_when(
      game_idx <= 4 ~ "Classic",
      game_idx %in% 5:7 ~ "Colonial",
      game_idx %in% 8:9 ~ "Urban",
      game_idx >= 10 ~ "Ancient/RPG"
    ),
    CatCommunity = factor(CatCommunity, levels = c("Classic", "Colonial", "Urban", "Ancient/RPG")),
    
    CatEngine = case_when(
      game_idx <= 4 ~ "Anvil",
      game_idx %in% 5:7 ~ "AnvilNext",
      game_idx >= 8 ~ "AnvilNext 2.0"
    ),
    CatEngine = factor(CatEngine, levels = c("Anvil", "AnvilNext", "AnvilNext 2.0")),
    
    NumGenerationHalfs = case_when(
      game_idx == 1 ~ 0.5,
      game_idx %in% 2:4 ~ 1.0,
      game_idx == 5 ~ 1.5,
      game_idx == 6 ~ 2.0,
      game_idx == 7 ~ 2.5,
      game_idx %in% 8:9 ~ 3.0,
      game_idx >= 10 ~ 4.0
    ),
    NumGenerationWholes = case_when(
      game_idx == 1 ~ 1,
      game_idx %in% 2:4 ~ 2,
      game_idx %in% 5:7 ~ 3,
      game_idx %in% 8:9 ~ 5,
      game_idx >= 10 ~ 5
    ))

```


```{r}
dff_eras |> 
  filter(game_idx != 1,
         CatCommunity == "Classic" | CatCommunity == "Ancient/RPG") |> 
  drop_na() |> 
  group_by(ResponseId, CatCommunity) |> 
  summarise(
    MeanRating = mean(Overall, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = CatCommunity,
    values_from = MeanRating
  ) %>%
  drop_na() |> 
  mutate(
    PreferenceDiff = `Classic` - `Ancient/RPG`
  ) |> 
  ggplot(aes(x = PreferenceDiff)) +
  geom_histogram(bins = 30)
  
# alternate plot?

# somehow augment with Total Played of each category contributing to their mean?
```

```{r}
# played at least one of both eras, what is the TotalPlayed of them?

# UGH THIS IS WRONG
dff_eras |> 
  filter(game_idx != 1,
         CatCommunity == "Classic" | CatCommunity == "Ancient/RPG") |> 
  group_by(ResponseId, CatCommunity) |> 
  summarize(CatGamesPlayed = sum(Played)) |> 
  pivot_wider(
    names_from = CatCommunity,
    values_from = CatGamesPlayed,
    values_fill = 0
  ) |> 
  drop_na()

# something is fishy about these counts
  
```

```{r}
# you only played one, what was it?
# MAKE THIS WAY NICER
#TODO: wrong spot
#TODO: reminds me to clean up df in similar fashion as other df's

df |> 
  filter(TotalPlayed == 1) |> 
  ggplot(aes(x = as.factor(IntroList))) +
  geom_histogram(stat = "count")
```



```{r}
library(purrr)
# note linear models are rough here b/c it's a 1-10 and is not really interval data esp. for interpretations

# does story or gameplay have a bigger impact on Overall?
summary(lm(Overall ~ Story + Gameplay, data = dff_eras))
summary(lm(Overall ~ Story*Gameplay, data = dff_eras))
# seems gameplay does. there is a bit of an interaction effect though (higher numbers, weaker links) but practically quite small b/c doesn't add much r^2


# loop through model within category (can replace CatCommunity with another)
tidy_models <- dff_eras %>%
  group_by(CatCommunity) %>%
  nest() %>%
  mutate(model = map(data, ~lm(Overall ~ Story + Gameplay, data = .x)))

tidy_models$model %>% map(summary)
# looking too see if within these categories story takes a more prominent role
# answer: gameplay generally still a bigger impact
```


```{r}

```


# Revisit Story and Gameplay trends

```{r}
dff_responses |> 
  filter(Subquestion == "Story") |> 
  mutate(GameNum = fct_recode(GameNum, !!!setNames(short_gamenames, community_gamenames))) |> 
  ggplot(aes(x = GameNum, y = Rating, fill = GameNum, color = GameNum)) +
  geom_violin(alpha = .7, quantile.linetype = 1, scale = "width", quantiles = 0.5) +
  theme_cowplot() + 
  scale_fill_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_color_manual(values = setNames(ac_palette, community_gamenames)) +
  theme(axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")) +
  scale_y_continuous(breaks = 1:10) +
  xlab("") +
  ylab("Story Game Rating") +
  labs(title = "Story Rating Distributions",
       subtitle = "Scaled to identical width, out of those who rated the game only")
```


```{r}
dff_responses |> 
  filter(Subquestion == "Gameplay") |> 
  mutate(GameNum = fct_recode(GameNum, !!!setNames(short_gamenames, community_gamenames))) |> 
  ggplot(aes(x = GameNum, y = Rating, fill = GameNum, color = GameNum)) +
  geom_violin(alpha = .7, quantile.linetype = 1, scale = "width", quantiles = 0.5) +
  theme_cowplot() + 
  scale_fill_manual(values = setNames(ac_palette, community_gamenames)) +
  scale_color_manual(values = setNames(ac_palette, community_gamenames)) +
  theme(axis.text.x = element_text(size = 10, angle = 40, hjust = .95, vjust = .95, face = "bold")) +
  scale_y_continuous(breaks = 1:10) +
  xlab("") +
  ylab("Gamplay Game Rating") +
  labs(title = "Gameplay Rating Distributions",
       subtitle = "Scaled to identical width, out of those who rated the game only")
```

I think gameplay complaints likely overblown. See how Valhalla is basically just AC3 all over again? At worst it's a syndicate, which is also normal. makes me wonder about shadows, lol


MAKE SOME TRENDLINES? INCLUDE RELEASE YEAR AS A VARIABLE? ETC? 

# Analysis

We will now proceed with our analysis.

```{r}

# MLR overall ~ story + gameplay (+ intxn?) or even per-group

# pearson/spearman correlation coefficients and heatmap of the same of overall scores

# PCA or cluster analysis on rating patterns, unsupervised?

# correlation coefficients of games played/co-occurrence

# ADD IN developer eras or time-eras
# potential groupings:
# mechanical: Social Stealth AC1 thru Rogue; Transition Unity and Syndicate; RPG trio
# narrative: Desmond AC1 thru AC3; Anthology AC4 thru Syndicate; Ancient trio
# engine: Anvil AC1 thru AC:Rev; AnvilNext AC3 thru Rogue; AnvilNext 2.0 Unity thru end, tho origins to val was rebuilt
# community: Classic AC1 thru Rev; Colonial AC3 thru Rogue; Urban Unity and Syndicate; RPG trio. Basically above.
# studio: all montreal except rogue-sofia, syndicate-quebec, odyssey-quebec
# think will bundle AC1 but if it's an outlier maybe split off (prob community schema only)
# maybe creative directors? but that's probably overkill
# can at least null = = = of means, but potentially others
# one-way ANOVA? 
# simple contrast RPG vs others
# or lump mids, so AC1-AC:R ezio AC3-Synd middle and then RPG, 3 is nice number
# interesting variant, half-steps: 0.5 = AC1, 1 = AC2-Rev, 1.5 = AC3, 2 = BF, 2.5 = Rogue, 3 = Unity/Synd, 4 = RPG

# create a variable that is year of setting? lol

# throw something ML at it

# story - gameplay delta

# years since release - nostalgia? including flexi curve?

```

```{r}
#| label: modeling

set.seed(1001)

summary(lm(Overall ~ Story*Gameplay, data = dff_eras))


```

# Conclusion

Analysis that is interesting but out of scope for me: sales and see if any correlations there. because requires a time series kind of thing maybe, and possibly controlling for consoles, steam vs internal, outdated numbers, etc.
