---
title: "EDA"
subtitle: "Exploring AC Survey"
author: "Dylan Bay"
date: today
format:
    html:
        toc: true
        df-print: paged
        code-fold: true  # Code hidden by default
        embed-resources: true
        code-summary: "Show the code"
theme: simplex
editor: visual
---

```{r}
#| label: setup
#| include: false

# From Cleaning.R
library(dplyr)
library(readr)
library(tidyr)
library(stringr)
library(sf)  
library(rnaturalearth) 
library(here)
library(lubridate)

# Loaded here
library(forcats)
library(ggplot2)
library(cowplot)
library(patchwork)
library(skimr)
library(naniar)

# Options
knitr::opts_chunk$set(  
fig.width = 8,
fig.height = 5,
fig.align = "center",
dpi = 300
) # beyond YAML defaults
options(scipen = 999)
theme_set(theme_cowplot())
```

# Introduction

I will be analyzing THIS data source. For some background, CONTEXT. The goal is to OBJECTIVE.

# Import

```{r}
#| label: load-data

source(here::here("Cleaning.R"))
```

# EDA

Here is some initial descriptive information about our dataset.

```{r}
#| label: skim_eda

# skim(df)
# df |> group_by(cat_var) |> skim()  # summaries per major category
# df |> skim() |> filter(n_missing > 0)  # summary of missings
# vis_miss(df)  # heatmap of missingness overall
# gg_miss_var(df)  # bar of missingness
# gg_miss_upset(df)  # easy col-to-col missingness associations

```

```{r}
#| label: country_eda

country.gg <- df %>%
   count(CountryName) %>%
  filter(n > 1) |> 
   ggplot(aes(x = n, y = fct_reorder(CountryName, n), fill = CountryName)) +
   geom_col() +
   labs(x = "Number of Responses (n > 1)", y = "Country") +
  theme(legend.position = "none")
subregion.gg <- df %>%
   count(Subregion) %>%
   ggplot(aes(x = n, y = fct_reorder(Subregion, n), fill = Subregion)) +
   geom_col() +
   labs(x = "Number of Responses", y = "Subregion")
wbregion.gg <- df %>%
   count(WBRegion) %>%
   ggplot(aes(x = n, y = fct_reorder(WBRegion, n), fill = WBRegion)) +
   geom_col() +
   labs(x = "Number of Responses", y = "World Bank Subregion")
country.gg 
subregion.gg
wbregion.gg
# note that WBRegion does not perfectly nest in Subregion due to a few MENA countries (Turkey, Israel, Saudi Arabia)
```

```{r}
df |> 
  filter(if_all(ends_with("_1"), is.na))  # req recent version: dpylr 1.2+
# 30 records didn't proceed to the second question - that's a 90.7% rate to pass to the next set. Decent.

# # let's see if we maybe have any problematic completions? 
# because remember we have a whole set of games-played only, and then full ratings... but did any FULL raters give up?
# this is kinda tricky to code with branching logic...

# To do this let's do a two-step transform of the grain: from respondent-rows, to individual response-rows
#  (with a metadata column identifying the question), then re-block (wider) as question-rows

df_long <- df |> 
  pivot_longer(
    cols = contains("_"),
    names_to = c("group", "question"),
    names_sep = "_"
  ) |> 
  pivot_wider(
    names_from = question,
    values_from = value
  )

# this answers: did anyone forget or decline to fill in one of the three subquestions (within a game) randomly?
partial_within_game <- df_long |> 
  filter(Intro == 1) |> 
  filter(is.na(`1`) | is.na(`2`) | is.na(`3`)) |>  
  select(c("ResponseId", "IntroList", "group", "Intro", `1`, `2`, `3`, "Progress", "Duration")) |> 
  filter((is.na(`1`) + is.na(`2`) + is.na(`3`)) < 3)
# yes, three people. will need to consider how to handle this, because will (slightly) affect a few calculations
# note that all three of these people DID fully rate all the rest, it's just these randomly missing single sub-q's
# c("R_1ikUGhQjZS6RZJt", "R_BPzLWS3pTSYFU2J", "R_Uu9SV5hqekMiW8V")

# usually, either someone drops the survey entirely when reaching the non-Intro question, OR fills it ALL out.
# this answers: did anyone fill out only SOME of the follow-ups?
partial_within_list <- df_long |> 
  filter(Intro == 1) |> 
  group_by(ResponseId) |>
  filter(
    any(is.na(`1`) & is.na(`2`) & is.na(`3`)) & 
    any(!is.na(`1`) | !is.na(`2`) | !is.na(`3`))
  ) |>
  ungroup()
# yes, two people neglected to answer one game, randomly
# c("R_1Ow4KSy0Od9qDxH", "R_3ncpah7gt2PAX4m")

```

Also remember I did some work on the shift in distribution

```{r}
library(dplyr)
library(effsize)

# 1. Bucket the days and drop the rest
df_bucketed <- df %>%
  mutate(DayBucket = case_when(
    RecordedDay == 24 ~ "Day 24",
    RecordedDay == 25 ~ "Day 25",
    RecordedDay %in% c(26, 27) ~ "Days 26-27",
    RecordedDay %in% c(28, 29) ~ "Days 28-29",
    TRUE ~ "Drop"
  )) %>%
  filter(DayBucket != "Drop") %>%
  mutate(DayBucket = factor(DayBucket, levels = c("Day 24", "Day 25", "Days 26-27", "Days 28-29")))

# 2. Generate all unique pairs of your buckets
buckets <- levels(df_bucketed$DayBucket)
pairs <- combn(buckets, 2, simplify = FALSE)

# 3. Calculate Cliff's Delta for each pair
results <- lapply(pairs, function(p) {
  # Subset data to just the two groups we are comparing
  subset_df <- df_bucketed %>% 
    filter(DayBucket %in% p) %>%
    mutate(DayBucket = droplevels(DayBucket)) # cliff.delta strictly expects exactly 2 levels
  
  # Run the test
  cd <- cliff.delta(TotalPlayed ~ DayBucket, data = subset_df)
  
  # Extract the useful bits into a clean row
  data.frame(
    Group_1 = p[1],
    Group_2 = p[2],
    Cliffs_Delta = round(cd$estimate, 3),
    CI_Lower = round(cd$conf.int[1], 3),
    CI_Upper = round(cd$conf.int[2], 3),
    Magnitude = as.character(cd$magnitude)
  )
})

# 4. Combine and view the results
cliff_results <- bind_rows(results)
print(cliff_results)

# this is % overlapping prob
# Instead of just saying "Day 1 and Day 2 are different," Cliff's Delta quantifies how much they overlap. It ranges from
# -1 to 1. A value of 0 means the distributions are completely overlapping; 1 or -1 means there is no overlap at all. It
# is incredibly easy to explain to an audience: "A randomly selected person from Day 1 has a 30% higher chance of having
# played more games than a person from Day 2."

# long story short: mostly there is a noticeable Day 1 effect, though still only so-so in strength
```


# Analysis

We will now proceed with our analysis.

```{r}
#| label: modeling

set.seed(1001)
```

# Conclusion

It is clear that FINDING. We recommend ACTION. Possible next steps include EXTRAS.
